Assigning Boy Scouts to Patrols

### 2016-06-03 poster/poster.tex

% Section and subsections will appear in the presentation overview
% and table of contents.
\begin{frame}{Problem Description}%{Optional Subtitle}
	\begin{itemize}
		\item Scoutmaster Gene Bruce of Troop 407 in Kent, Washington must assign new boy scouts into their patrols. In these patrols, the scouts engage in numerous activities and form close bonds. \\
		\vspace{0.2in}
		\item The number of incoming scouts are increasing requiring multiple patrols to better organize activities and to form a small community between scouts.
		The younger scouts are temperamental and awkward when dealing with adversity, ruining their experience and causing many to quit. \\
		\vspace{0.2in}
		\item \textbf{Goal:  Assign 13 boy scouts of appropriate size (of 6-8 scouts) to two patrols such that we maximize the retention rate of the scouts by avoiding severe conflicts and maximizing positive relationships between scouts.}
	\end{itemize}
\end{frame}

>>>>

% Section and subsections will appear in the presentation overview
% and table of contents.
\begin{frame}{Problem Description}%{Optional Subtitle}
	\begin{itemize}
		\item Scoutmaster Gene Bruce of Troop 407 in Kent, Washington must assign new boy scouts into their patrols. In these patrols, the scouts engage in numerous activities and form close bonds. \\
		\vspace{0.2in}
		\item The number of incoming scouts are increasing, requiring multiple patrols to better organize activities and to form a small community between scouts.
		The younger scouts are temperamental and awkward when dealing with adversity, ruining their experience and causing many to quit. \\
		\vspace{0.2in}
		\item \textbf{Goal:  Assign 13 boy scouts of appropriate size (of 6-8 scouts) to two patrols such that we maximize the retention rate of the scouts by avoiding severe conflicts and maximizing positive relationships between scouts.}
	\end{itemize}
\end{frame}
